Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-21 sections/intro.tex
Update on Overleaf.

\begin{enumerate}
\item 
\teo{How about:
A Looplet based level-format abstraction.
Although many systems (TACO, Taichi, SPF, Ebb) features a flexible data structure description language for array-like computations, we show that we can describe more level formats than any other by a level format abstraction designed to target Looplets in the context of an array programming language with fine-grained control flow. The first such set of formats to efficiently capture banded,
triangular, run-length-encoded, or sparse datasets, and any combination thereof.
}

>>>>

\begin{enumerate}
\item 
\teo{How about:
A Looplet based level-format abstraction.
Although many systems (TACO, Taichi, SPF, Ebb)~\cite{chou2018format,  hu_taichi_2019, strout2018sparse, bernstein2016ebb} features a flexible data structure description language for array-like computations, we show that we can describe more level formats than any other by a level format abstraction designed to target Looplets in the context of an array programming language with fine-grained control flow. The first such set of formats to efficiently capture banded,
triangular, run-length-encoded, or sparse datasets, and any combination thereof.
}
